Single Site, Single Disturbance

### 2021-02-02 Paper.Rmd
Pushed results outline to own file, small updates to discussion and methods

# Results

1. Simulated data experiments (known disturbance)
  + Single Site, Single Disturbance

Figures showing the current problem, solution, and that we've got a genuine multimodal distribution and P(dist)

  + SSSD Multi Pool

Figures showing pool cov, C accounting / attribution

  + SS Multi-Disturbance w/ PFT switching

Figure showing PFT switching vs not, ability to detect disturbance type

  + Simple Multi-site: spatial cov

Figure showing "dragging down" of neighbors in conventional and breaking of COV in Multinomial

2. Real-world examples
  + Calibrate state-and-transition prior
    * data: (samples from) maps of disturbance type by year
    * model: Multinomial Dirlichet

Figure showing map and estimated priors

  + Applications
    + Logging
    + Fire
    + Land use transition (forest -> non?)

>>>>

<!---- RESULTS --->
```{r child = 'results.Rmd'}
```

### 2021-02-02 discussion.Rmd
two site model. Some text
Pushed results outline to own file, small updates to discussion and methods

@@

* Future directions
  * Disturbance priors need to be spatially heterogenous and evolve temporally
    * Connect to state-and-transition literature
  * Scaling up -> spatially implicit
    * ED2
    * Contagion

>>>>

* Discussion of similar approaches
[@Ye2020]

@@

* Future directions
  * Disturbance priors need to be spatially heterogenous and evolve temporally
    * Connect to state-and-transition literature
    * shared spatial information (e.g. dispersal kernels)
  * Scaling up -> spatially implicit
    * ED2
    * Contagion

* OREGON: FUTURE DIR
  * disturbance products are 'seeing' more than is in AGB product alone
    * also would benifit from more products (e.g. LAI)
  * would be good to add 'memory' to algorithm so further evidence of disturbance reinforces initial detection (similar to BLC); would allow reduction in time step and greater sensor fusion

* Run just the Assimilation step for simulated disturbance that vary in magnitude, process error, observation error, etc to detect sensitivity
* Approximation of not simulating disturbed ensemble members and relying SOLEY on ensemble adjustment
* Analytical approximation of sequential beta-binomial then KF vs full joint model
